Review of Assigned Readings

### 2018-01-04 paper/paper.tex
solve brandtwilliams2007 reference issue

%************************** Specify bibliography package **************************
\usepackage{csquotes}
\usepackage[style=apa,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

@@

\subsection{Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandt_williams_2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

>>>>

%************************** Specify bibliography package **************************
\usepackage{csquotes}% Recommended
\usepackage[style=apa]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

@@

\subsection{Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}). The calculations of these criteria for our specific data set are shown in the following table.\\
